### 2019-04-02 papers/journal/prelim.tex
Uniform use of the title without :

We will use lower case variables like $e,r,s$ etc to represent vectors of
Boolean variables, possibly indexed, with multiple dimensions.
%
For example, $r_{ij}$ is a Boolean variable for index $(i,j)$.
%
%
A Boolean variable may take Boolean values $1$ or $0$.
%
The binary Boolean operators $\land$, $\lor$, and $\limplies$ are usually defined.
%
$\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over
collection of formulas respectively.
%
We will use the variables and operators to construct Boolean formulas to
encode our problems.
%
An assignment is a map from the variables in the formula to the Boolean values.
%
An assignment may satisfy a formula if the interpretation of Boolean operators
reduce the whole Formula into 1.
%
The problem of finding a satisfying assignment for a Boolean formula is known to be hard~\cite{cook1971complexity}.
%

@@

\subsection{Solvers}
In this paper, we will encode several problems into finding satisfying
solutions of a Boolean formula or QBFs.
%
We will use BMC, SMT and QBF solvers to get the satisfying assignments.
%
The modern solvers are result of several decades of research
and implement sophisticated algorithms.
%
A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{biere2009conflict}.
%1
The QBF solver add support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.

>>>>

\noindent We will use lower case variables like $e,r,s$ etc to represent vectors of
Boolean variables, possibly indexed, with multiple dimensions.
%
For example, $r_{ij}$ is a Boolean variable for index $(i,j)$.
%
%
A Boolean variable may take Boolean values $1$ or $0$.
%
The binary Boolean operators $\land$, $\lor$, and $\limplies$ are usually defined.
%
$\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over
collection of formulas respectively.
%
We will use the variables and operators to construct Boolean formulas to
encode our problems.
%
An assignment is a map from the variables in the formula to the Boolean values.
%
An assignment may satisfy a formula if the interpretation of Boolean operators
reduce the whole Formula into 1.
%
The problem of finding a satisfying assignment for a Boolean formula is known to be hard~\cite{cook1971complexity}.
%

@@

\subsection{Solvers}
\noindent In this paper, we will encode several problems into finding satisfying
solutions of a Boolean formula or QBFs.
%
We will use BMC, SMT and QBF solvers to get the satisfying assignments.
%
The modern solvers are result of several decades of research
and implement sophisticated algorithms.
%
A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{biere2009conflict}.
%1
The QBF solver add support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.

### 2019-04-02 papers/journal/problem.tex
Uniform use of the title without :

This section will present the different search problems of VTS.
%
We categorize the search problems into three different categories, search problem for existential condition, search problem for universal condition,
and performing synthesis on the incomplete VTS.

\subsection{Existential condition}
We employ two techniques to examine the existential condition. 
%
First, using the bounded model checking (BMC) technique~\cite{biere1999symbolic1, biere2003bounded}.
%
%It  represents the executions of a program symbolically and 
%
%The Bounded model checking technique
BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed positive integer value $w$ (\textit{unwinding depth}). 
%
The bounded execution is represented symbolically as a propositional formula and solved using a SAT solver.
% is used to check the satisfiability of the resultant propositional formula.
%
In case there is no violation for a particular depth, one can progressively increase the depth until either property is violated, the problem becomes intractable, or an upper bound of the system is reached, indicating the satisfiability of the property.
%
For our case, the unwinding depth is the length of the path of the underline graph.
%
%
For the experimentation, we restrict the check only to the elementary cycles; cycles of length one. 
%
This restriction puts an upper limit of number of nodes, $N$ on the length of the searched path. 
%
%
%and the upper bound is the number of nodes $N$.

@@

\subsection{Universal condition}
%Here we will present the QBF.
We will model the search problem for the universal condition as a quantified Boolean formula (QBF)~\cite{buning2009theory, benedetti2008qbf}, and resultant formula will be solved with the help of a QBF solver.
%
The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifiers.
%
The QBFs enables potentially more succinct encodings than SAT but with a higher complexity class decision problem~\cite{buning2009theory}.

@@

%\subsection{Problem Statements}
\subsection{Synthesis of VTS}
%
We also consider another variant of analysis of VTSs.
%
We will assume that we are given a VTS, whose all components
are not specified.
%
Our objective is to find the missing parts.
%
The missing parts can be in any of the components of VTS. 
%
For example, some undiscovered edges or nodes, or insufficient
knowledge about the presence of molecules in some part of the VTS.
%
To cover most of the likely variations of this missing information,
we have encoded the following variants of VTS synthesis problem.

@@

\subsubsection{Synthesis problem}

>>>>

\noindent This section will present the different search problems of VTS.
%
We categorize the search problems into three different categories, search problem for existential condition, search problem for universal condition,
and performing synthesis on the incomplete VTS.

\subsection{Existential condition}
\noindent We employ two techniques to examine the existential condition. 
%
First, using the bounded model checking (BMC) technique~\cite{biere1999symbolic1, biere2003bounded}.
%
%It  represents the executions of a program symbolically and 
%
%The Bounded model checking technique
BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed positive integer value $w$ (\textit{unwinding depth}). 
%
The bounded execution is represented symbolically as a propositional formula and solved using a SAT solver.
% is used to check the satisfiability of the resultant propositional formula.
%
In case there is no violation for a particular depth, one can progressively increase the depth until either property is violated, the problem becomes intractable, or an upper bound of the system is reached, indicating the satisfiability of the property.
%
For our case, the unwinding depth is the length of the path of the underline graph.
%
%
For the experimentation, we restrict the check only to the elementary cycles; cycles of length one. 
%
This restriction puts an upper limit of number of nodes, $N$ on the length of the searched path. 
%
%
%and the upper bound is the number of nodes $N$.

@@

\subsection{Universal condition}
%Here we will present the QBF.
\noindent We will model the search problem for the universal condition as a quantified Boolean formula (QBF)~\cite{buning2009theory, benedetti2008qbf}, and resultant formula will be solved with the help of a QBF solver.
%
The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifiers.
%
The QBFs enables potentially more succinct encodings than SAT but with a higher complexity class decision problem~\cite{buning2009theory}.

@@

%\subsection{Problem Statements}
\subsection{Synthesis of VTS}
%
\noindent We also consider another variant of analysis of VTSs.
%
We will assume that we are given a VTS, whose all components
are not specified.
%
Our objective is to find the missing parts.
%
The missing parts can be in any of the components of VTS. 
%
For example, some undiscovered edges or nodes, or insufficient
knowledge about the presence of molecules in some part of the VTS.
%
To cover most of the likely variations of this missing information,
we have encoded the following variants of VTS synthesis problem.

@@

\subsubsection{Synthesis problem.}
